Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-04-04 paper/ms.tex
updated paragraphs in discussion about median and widths

\begin{figure}
\includegraphics[width=0.47\textwidth]{fig4.pdf}
\caption{Median mass, $\log M_{50}$, and mass width $\Delta
  M_{1\sigma}=\log M_{84} - \log M_{16}$, for all models with low
  $\chi^2_{\mathcal{M}}/2 < 1.0$. The median mass spans two orders of
  magnitude with a mean value around $10^{10.5}$\hMsun. The
  width has a median of $0.3$ dex (a factor of $2$ in
  mass) with a maximum value of $0.7$ dex (a factor of 5). This means
  that all models consistent with observations have a very narrow
  range in halo mass where the LAEs are expected to be hosted.} 
\label{fig:mmed}
\end{figure}

@@

In Fig. \ref{fig:mmed} we show the $\log M_{50}$-$\Delta M_{1\sigma}$
plane for the models selected in the $1\sigma$ posterior region for
\mmin. The color encodes the $\mmin$ value.

The points are color coded according to their
\dlm\ associated value. We can see that the median mass ($M_{50}$) and
$M_{84}$ are not very sensitive to  $\lmmax=\lmmin +\dlm$ specially
when $\dlm\gtrsim1.0$dex. We particularly found that
$\lmmin\lesssim\log M_{50}\lesssim\lmmin+0.2\rm{dex}$ and that
$\lmmin+0.1\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+0.5\rm{dex}$
regardless of the value of \dlm. The latter is a consequence of the
very steepen distribution of the dark matter mass function  and is at
the same time the reason for the almost perfect one to one relation
between \mmin\ and \focc. However, it can also be seen in
Fig. \ref{fig:mmed} that $\log M_{84}$ is very sensitive to \lmmax
($\lmmin+0.2\rm{dex}\lesssim\log
M_{50}\lesssim\lmmin+1.5\rm{dex}$). Thereby, any differences in the
clustering strength of models sharing the same \mmin but different
\mmax should be mainly driven by the  $\sim16\%$ most massive  halos
of each model $\mathcal{M}$.

In order to estimate the effect of most massive halos in
$ACF_{\mathcal{M}}$ in Fig. \ref{fig:corr} we show the computed
$ACF_{\mathcal{M}}$ of models with $\lmmin=0.5$ and different values
of $\dlm$. We can see that the clustering gets stronger for larger
values of \dlm. Nevertheless, due to the large impact of cosmic
variance at the volume of the current observations all the models  are
basically consistent within errors. The last result together with the
large Poissonian observational error in the ACF explain the current
difficulty to put tighter constrains in \lmmax\ in our model.

 In Fig. \ref{fig:mmed} the green vertical lines represent  the 16, 50
 and 84 percentiles  of the posterior probability distribution of
 \mmin that we previously obtained. From this figure we find that the
 median dark matter halo mass is $\tilde{M}_{\mathrm h} =
 10^{10.6^{+0.7}_{-0.6}} $. 
This result is consistent with previous
 estimations of  the  median dark matter halo mass reported by
 \citet{Bielby16} ($\tilde{M}_{\mathrm h} = 10^{11.0\pm0.6}$),
 \citet{Gawiser07} ($\tilde{M}_{\mathrm h} = 10^{10.9\pm0.9}$) and
 \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} =
 6.7^{+42.0}_{6.7}\times10^{10}$) using semi-analitical approaches.

>>>>

\begin{figure}
\includegraphics[width=0.47\textwidth]{fig4.pdf}
\caption{Median mass, $\log M_{50}$, and mass width $\Delta
  M_{1\sigma}=\log M_{84} - \log M_{16}$, for all models with low
  $\chi^2_{\mathcal{M}}/2 < 1.0$. The median mass spans two orders of
  magnitude with a mean value around $10^{10.5}$\hMsun. The
  mass width $\Delta M_{1\sigma}$ has a median of $0.3$ dex (a factor
  of $2$ in mass) with a maximum value of $0.7$ dex (a factor of
  5). This means that all models consistent with observations have a
  very narrow range in halo mass.}
\label{fig:mmed}
\end{figure}

@@

In Fig. \ref{fig:mmed} we show the $\log M_{50}$-$\Delta M_{1\sigma}$
plane for the models selected to have $\chi^{2}_{\mathcal{M}}/2 < 1$,
which roughly correspond to the $1\sigma$ region in the posterior
distribution for the model parameters. The color encodes the
$\chi^{2}_{\mathcal{M}}/2$ value. The median mass has a wide distribution
spanning two orders of magnitude.

From this distribution we obtain $\log M_{50} = 10.5\pm 0.6$ or
equivalently $M_{50} = 3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.  
The $1\sigma$ uncertainty for this median value is estimated from the
$16$ and $84$ percentile values in the $\log M_{50}$ distribution.  
This result is consistent with previous
 estimations of  the  median dark matter halo mass reported by
 \citet{Bielby16} ($\tilde{M}_{\mathrm h} = 10^{11.0\pm0.6}$),
 \citet{Gawiser07} ($\tilde{M}_{\mathrm h} = 10^{10.9\pm0.9}$) and
 \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} =
 6.7^{+42.0}_{6.7}\times10^{10}$) using semi-analitical approaches.

However, the same Figure \ref{fig:mmed} shows something interesting
that semi-analytical approaches were not able to predict.
The mass width, $\Delta M{1\sigma}$, that is the width of the mass
distribution for a given model with fixed $\mmin$ and $\mmax$, has a
median value and $1\sigma$ uncertainty of $\Delta M{1\sigma} =
0.55^{+0.11}_{-0.31}$ dex.
This means that the mass range for halos hosting LAEs is very narrow,
there is only a factor of $2$ to $4$ between the lower and upper mass
boundary.

In summary, the median mass could be anything in the range
$10^{9.5}$\hMsun and $10^{11.5}$, but the width is highly constrained
to be between $0.2$ and $0.6$ dex.

In Fig. \ref{fig:corr} we show the computed
$ACF_{\mathcal{M}}$ of models with $\lmmin=0.5$ and different values
of $\dlm$. We can see that the clustering gets stronger for larger
values of \dlm. Nevertheless, due to the large impact of cosmic
variance at the volume of the current observations all the models  are
basically consistent within errors. The last result together with the
large Poissonian observational error in the ACF explain the current
difficulty to put tighter constrains in \lmmax\ in our model.
